Current model cost effect

### 2020-09-22 src/current_model_effect.Rmd
prob cut wrong way twice :-)

```{r}
#cut prediction.probs with seq(0, 1, .1)
x <- seq(0.1, .9, .1)
pred.classes <- data.frame(matrix(nrow=nrow(df),ncol=length(x)))
colnames(pred.classes) <- paste0("p_",x)
for (i in x ) {
  pred.classes[,paste0("p_",i)] <-  factor( df$Deferred <= i ,labels = c("Deferred","Accepted"))
}

@@

@@

>>>>

```{r}
#cut prediction.probs with seq(0, 1, .1)
x <- seq(0.1, .9, .1)
pred.classes <- data.frame(matrix(nrow=nrow(df),ncol=length(x)))
colnames(pred.classes) <- paste0("p_",x)
for (i in x ) {
  pred.classes[,paste0("p_",i)] <-  factor( df$Deferred >= i ,labels = c("Accepted","Deferred"))
}

@@

```{r}
summary(pred.classes)
```

@@

tprs
```
